\documentclass{moderncv}

\moderncvstyle{fancy}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[polish]{babel}

\usepackage[left=0.3in, right=1in, top=1in, bottom=1in]{geometry}
\setlength{\hintscolumnwidth}{4.78cm}
\recomputelengths

\name{Krzysztof}{Gutkowski}
\title{Fullstack Developer}
\phone[mobile]{+48 500 535 818}
\email{krzysio.gutkowski@gmail.com}
\social[github]{LiquidPL}

\begin{document}

\makecvtitle

\section{Career summary}
\cvitem{}{I am a Fullstack Developer with 9 years of experience in PHP, and 5 years in JavaScript/TypeScript. I specialize in Laravel and Symfony on the backend side, and React on the frontend. I've been also recently focusing on learning Vue and Angular. I have experience in working with large projects, both modern and legacy.}

\section{Commercial experience}
\cventry{2020/10 - 2024/08}{backend PHP developer}{Macopedia}{remote/Poznan, Poland}{}{
    \begin{itemize}
        \item developed and maintained projects for various clients:
        \begin{itemize}
            \item content management system (TYPO3/Symfony),
            \item custom B2B eCommerce portal (Symfony),
        \end{itemize}
        \item worked on plugins for TYPO3,
        \item developed patches for the upstream TYPO3 project.
    \end{itemize}
}
\cventry{2019/11 - 2020/03}{PHP/full-stack developer}{mediacyfrowe.pl - doradztwo, realizacja}{Warsaw, Poland}{}{
    \begin{itemize}
        \item maintained projects for various clients,
        \item worked on the company's own projects (in this case, custom authored plugins for popular self-hosted systems, ie. WordPress, PrestaShop),
        \item performed onsite maintenance of services developed for various clients (one notable instance being a ticket sale and scanning system developed for a large trade fair in Warsaw).
    \end{itemize}
}
\cventry{2016 - 2019}{Laravel/React developer}{osu! (\textit{\href{https://osu.ppy.sh}{https://osu.ppy.sh}})}{remote}{}{
    % Frontend and backend development for the website of a video game (around 1 million of monthly active users).
    Participated in a rewrite of the legacy website (built on top of \textit{phpBB} and API/backend for an online game (approx. 1 million monthly active users)) based on a Laravel/React stack.
    \begin{itemize}
        \item adapted various existing database tables to ORM models,
        \item implemented new components/pages in React, alongside the necessary API endpoints,
        \item focused on maintaining compatibility with the legacy website (both websites were running concurrently, using the same production database).
    \end{itemize}
}
\cventry{2019 - teraz}{network administrator/developer}{cavoe's osu! event (COE)}{online/Den Bosch, Netherlands}{volunteering}{
    IT and programming support for a mass event (approx. 1000 guests across 7 days) focused around video games.
    \begin{itemize}
        \item planned and deployed the physical network and configured routers/switches/access points/etc.,
        \item implemented various broadcast graphics and panels used during livestreams on Twitch (Vue),
        \item developed and maintained the event's website, containing various information and the ticketing system (NestJS + Angular).
    \end{itemize}
}
\cventry{2015 - now}{Linux systems administrator}{VI LO im. Jana Kochanowskiego}{Radom}{}{Maintaining the system used for handling computer science\slash programming classes and algorithmic contests ran by my high school.}

\section{Education}
\cventry{2020/10 - 2025/10}{engineer's degree}{Faculty of Electronical Engineering, Warsaw University of Technology}{Warsaw}{}{Applied Computer Science}

\section{Skills}
\cvitem{Programming languages}{
    \begin{itemize}
        \item PHP - advanced (approx. 9 years)
        \item JavaScript/TypeScript - proficient (approx. 5 years)
        \item Python - intermediate
        \item C++ - intermediate
        \item Rust - beginner
    \end{itemize}
}
\cvitem{Backend frameworks}{
    \begin{itemize}
        \item Laravel - advanced (approx. 4 years)
        \item Symfony - advanced (approx. 5 years)
    \end{itemize}
}
\cvitem{Frontend technologies}{
    \begin{itemize}
        \item React - proficient (approx. 4 years)
        \item Vue, Angular - beginner
        \item Less/SCSS
    \end{itemize}
}
\cvlanguage{Polish}{native}{}
\cvlanguage{English}{CEFR C1}{Cambridge Certificate in Advanced English}


\section{Personal interests}
\cvlistdoubleitem{Books (fantasy, science fiction)}{Cycling}
\cvlistdoubleitem{Swimming}{Alpine skiing}
\cvlistitem{Video games}

\vfill
\begin{center}
\textit{\small I agree to the processing of personal data provided in this document for realising the recruitment process pursuant to the Personal Data Protection Act of 10 May 2018 (Journal of Laws 2018, item 1000) and in agreement with Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of natural persons with regard to the processing of personal data and on the free movement of such data, and repealing Directive 95/46/EC (General Data Protection Regulation).}
\end{center}

\end{document}
